\thispagestyle{plain}
\begin{center}
    \LARGE
    \textit{\textbf{Acknowledgements}}
        
    \vspace{0.4cm}
\end{center}
\normalsize

\vspace{0.9cm}

First and foremost, I would like to express my deepest gratitude to Professor Theodoros Samaras for his support and guidance throughout every stage of this work. I am equally indebted to PhD candidate Dimitris Stoupis, whose expertise in academic matters, neuroscience, neuroanatomy, coding and statistics was instrumental in navigating the complexities of this research. His constant assistance and acumen were crucial to the successful completion of this project.

Beyond the technical work and analysis, the review process is crucial to ensuring the highest quality outcome. For this, I am profoundly grateful to my significant other, Ioanna-Anastasia Koukouli, for her unwavering support and encouragement throughout this journey. Her key insights into the design of this thesis were instrumental in shaping the final work, and her thoughtful input greatly enriched the overall direction of the project.

In any research endeavor, there are often unsung heroes who play a vital role behind the scenes. I believe it is essential to acknowledge them here. The open knowledge and open-source communities deserve special recognition for their immediate and high-quality support, whether through forums or mailing lists. Their collective wisdom greatly aided in resolving various technical challenges. I hope all contributors have been given the deserved credit.

\vspace*{\fill}

