@article{Edens2010,
   abstract = {Background: Although African Americans (AAs) smoke fewer average cigarettes per day (CPD) than European Americans (EAs), they carry a disproportionate tobacco-related morbidity and mortality burden. The objective of this study was to evaluate the ethnic differences in markers of nicotine addiction, including rates of lifetime nicotine dependence (ND) symptoms, current smoking, and smoking during pregnancy across different levels of peak lifetime cigarette consumption. Methods: Data from 237 EA (N = 118) and AA (N = 119) mothers participating in the Missouri Family Study (2003-2005), an ethnically diverse family study of offspring outcomes in high and low risk families, were used to contrast prevalence of ND symptoms and other smoking behaviors between EA and AA women at low (1-10 CPD), moderate (11-19 CPD), and high (≥20 CPD) levels of lifetime peak daily cigarette consumption. Results: Compared with EA smokers, AAs had lower lifetime prevalence of DSM-IV ND (68\% vs 54\%, P < 0.05), consumed fewer CPD during their heaviest lifetime consumption (18\% EA vs 58\% AA smoked ?10 CPD, P < 0.0001), but did not differ in overall rates of smoking during pregnancy or current smoking. However, stratifying by categories of peak lifetime daily cigarette use, AA mothers who smoked ?10 CPD reported greater lifetime ND symptoms and current smoking than their EA counterparts. In addition, nearly two thirds of AA mothers in this smoking category smoked during pregnancy, and 30\% smoked throughout an entire pregnancy. The respective prevalence estimates in EA mothers were 38\% and 0\%. Conclusions: Stratifying the sample into categories of lifetime peak daily cigarette use revealed significant ethnic or racial differences in smoking prevalence during pregnancy, which were obscured in overall analysis. Substantial public health risks warranting clinical attention exist among light smokers, particularly AA women. Copyright © 2010 American Society of Addiction Medicine.},
   author = {Ellen L. Edens and Anne L. Glowinski and Michele L. Pergadia and Christina N. Lessov-Schlaggar and Kathleen K. Bucholz},
   doi = {10.1097/ADM.0B013E3181AF111E},
   issn = {19320620},
   issue = {1},
   journal = {Journal of Addiction Medicine},
   keywords = {African American,Light smoker,Nicotine dependence,Pregnancy,Women},
   month = {3},
   pages = {55-60},
   title = {Nicotine addiction in light smoking African American Mothers},
   volume = {4},
   url = {https://journals.lww.com/journaladdictionmedicine/fulltext/2010/03000/nicotine_addiction_in_light_smoking_african.8.aspx},
   year = {2010},
}
